Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\begin{table}[]
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\ \hline
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\ \hline
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms  \\ \hline
	\end{tabular}
\end{table}

>>>>

Tab. \ref{aggregate} shows the result of the Aggregation Analysis approach which will be useful in determining the possible root cause of the regression. This approach will be used to fullfil the second needs of the PRA system.
\begin{table}[!htb]
	\caption{Aggregation Analysis result}
	\label{aggregate}
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\ \hline
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\ \hline
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms  \\ \hline
	\end{tabular}
\end{table}

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. by
In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for
stable application activity data that can be used as a baseline
or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, namely the latency data of all recorded traces
by the tracing system, and operating data that occurs on the critical path of all traces along with
its latency value which will be stored as a key-value pair as well.
